30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-18 paper.tex
"The implemention" is singular, so "a means" instead of "means"

	The implementation of The Onion Router was first described by the U.S. Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.

>>>>

	The implementation of The Onion Router was first described by the U.S. Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
